Non-nearest Neighbour ICD in Clusters

### 2016-03-17 revised/abstract.tex
format of the paper - prepare submission

\begin{abstract}
Interatomic Coulombic Decay (ICD) is an electronic decay process of
excited, ionized systems. It has been shown to occur in a multitude of small
and large systems.
The effects of more than one possible decay
partner are discussed in detail illustrated by simulated ICD electron spectra
of NeAr clusters and pure Ne clusters.
Hereby, the mostly underestimated contribution of decay with
non-nearest neighbours is highlighted. In the neon clusters, the lifetime of the
bulk atoms is found to be in excellent agreement with experiment, while the
lifetimes of the surface atoms differ significantly. Hence, the experimental
lifetime can not purely be explained by the effect of the number of
neighbours.

>>>>

\begin{abstract}
Interatomic Coulombic Decay (ICD) is an electronic decay process of
excited, ionized systems. It has been shown to occur in a multitude of small
and large systems.
The effects of more than one possible decay
partner are discussed in detail illustrated by simulated ICD electron spectra
of NeAr clusters and pure Ne clusters.
Hereby, the mostly underestimated contribution of decay with
non-nearest neighbours is highlighted. In the neon clusters, the lifetime of the
bulk atoms is found to be in excellent agreement with experiment
(\emph{Phys. Rev. Lett.}, \textbf{93}, 173401 (2004).), while the
lifetimes of the surface atoms differ significantly. Hence, the experimental
lifetime can not purely be explained by the effect of the number of
neighbours.

### 2016-03-17 revised/computational.tex
format of the paper - prepare submission

\section{Computational Details}
\label{sec:computational}
The cluster structures used were constructed to have an ideal icosahedral or
face-centered-cubic geometry with optional additional incomplete outermost
shells. These are based on the van der Waals radii for neon
$r_{Ne}=\unit[1.54]{\AA}$
and argon $r_{Ar}=\unit[1.88]{\AA}$ \cite{Bondi64}.
In case of the NeAr clusters two of those
cluster structures from Ref. \cite{Fasshauer14_1}, where the theoretical
and experimental argon content in the cluster,
the NeAr-ICD to total
ICD ratio and the peak position of the NeAr-ICD peak matched best for a given
manifold (set) of clusters produced under certain experimental conditions,
have been chosen.
These are $C_{Ar}=3$, $C_{Ne}=1$, $S_{Ne}=7$ for set 3
and $C_{Ar}=2$, $C_{Ne}=1$, $S_{Ne}=13$ for set 5 where we used the same
nomenclature as in Ref. \cite{Fasshauer14_1}. Hence, $C_{Ar}$ denotes
the edge length of the argon core, $C_{Ne}$ denotes the number of complete
neon shells around the argon core and $S_{Ne}$ denotes the number of 
triangular surfaces additionally covered by neon atoms.

@@

The calculations to obtain the ICD electron spectra of those cluster
structures were performed with
the program HARDRoC \cite{HARDRoC} using experimental ionization energies shown
in Table \ref{table:exp_input} and curves fitted to the decay width of the
NeNe ICD of Ref. \cite{Averbukh06_1} and the NeAr decay widths of Ref.
\cite{Fasshauer14_1}. These fitted curves yield lifetimes
$\tau=\frac{\hbar}{\Gamma}$ at the corresponding equilibrium distances of
$\tau_{NeNe}= \unit[60]{fs}$ and
$\tau_{NeAr}= \unit[44]{fs}$.

>>>>

\section{Computational Details}
\label{sec:computational}
The cluster structures used were constructed to have an ideal icosahedral or
face-centered-cubic geometry with optional additional incomplete outermost
shells. These are based on the van der Waals radii for neon
$r_{Ne}=$ \unit[1.54]{\AA}
and argon $r_{Ar}=$ \unit[1.88]{\AA} \cite{Bondi64}.
In case of the NeAr clusters two of those
cluster structures from Ref. \cite{Fasshauer14_1}, where the theoretical
and experimental argon content in the cluster,
the NeAr-ICD to total
ICD ratio and the peak position of the NeAr-ICD peak matched best for a given
manifold (set) of clusters produced under certain experimental conditions,
have been chosen.
These are $C_{Ar}=3$, $C_{Ne}=1$, $S_{Ne}=7$ for set 3
and $C_{Ar}=2$, $C_{Ne}=1$, $S_{Ne}=13$ for set 5 where we used the same
nomenclature as in Ref. \cite{Fasshauer14_1}. Hence, $C_{Ar}$ denotes
the edge length of the argon core, $C_{Ne}$ denotes the number of complete
neon shells around the argon core and $S_{Ne}$ denotes the number of 
triangular surfaces additionally covered by neon atoms.

@@

The calculations to obtain the ICD electron spectra of all cluster
structures were performed with
the program HARDRoC \cite{HARDRoC} based on the decomposition of the cluster into
pairs. Every pair with the same distance is treated equally. This includes the
assumption that every neon atom is ionized with the same probability.
\cite{Fasshauer14_1,Fasshauer_thesis}
It uses experimental ionization energies shown
in Table \ref{table:exp_input} and curves fitted to the decay width of the
NeNe ICD of Ref. \cite{Averbukh06_1} and the NeAr decay widths of Ref.
\cite{Fasshauer14_1}. These fitted curves yield lifetimes
$\tau=\frac{\hbar}{\Gamma}$ at the corresponding equilibrium distances of
$\tau_{NeNe}= \unit[60]{fs}$ and
$\tau_{NeAr}= \unit[44]{fs}$.

### 2016-03-17 revised/summary.tex
format of the paper - prepare submission

We have discussed two of the three aspects one needs to take into account
to simulate the ICD spectrum of rare gas clusters in detail. Due to the nature
of clusters, a neon atom ionized in the inner-valence will have several decay
partners at different distances. The larger the interatomic distance the higher
is the kinetic energy of the ICD electrons which will yield a multitude of
peaks in the spectrum. These are then weighted by the decay width, which
depends on the interatomic distance of the decay partners but also needs
to be scaled by the number of pairs of the same distance.
The manifold of all different decay events will then yield the spectrum.

When applying these aspects to cluster structures, one finds that not only
the nearest neighbours contribute to the spectrum, but several other decay
partners do as well. Decay partners until a distance of at least twice the
distance of the clostest decay partners should be taken into account.
In clusters with an icosahedral cluster structure this is especially important
because the smallest interatomic distance between atoms of the same and atoms
of different layers is different, but both distances are comparable.
This leads to a different number of peaks in the spectra which might help to
differentiate between clusters of icosahedral and cuboctahedral cluster structure.

While the theoretical lifetime of the bulk atoms show an excellent agreement
with experiment, the lifetimes of the surface atoms differ significantly.
Assuming the experimentally determined lifetime to be correct, this deviation
might be caused by different static cluster structures than taken into account
in this work, by different energetic stabilization of charges or by nuclear
dynamics. Which of these reasons explains the experiment can not be determined
at the moment. Experimentally determined photoelectron spectra of the outer
valence of high resolution in neon clusters would help to solve this puzzle.

>>>>

We have discussed two of the three aspects one needs to take into account
to simulate the ICD spectrum of rare gas clusters properly. Due to the nature
of clusters, a neon atom ionized in the inner-valence will have several decay
partners at different distances. The larger the interatomic distance is the higher
is the kinetic energy of the ICD electrons which will yield a multitude of
peaks in the spectrum. These are then weighted by the decay width, which
depends on the interatomic distance of the decay partners but also needs
to be scaled by the number of pairs of the same distance.
The manifold of all different decay events will then yield the spectrum.

When applying these aspects to cluster structures, one finds that not only
the nearest neighbours contribute to the spectrum, but several other decay
partners do as well. Decay partners until a distance of at least twice the
distance of the clostest decay partners should be taken into account.
In clusters with an icosahedral cluster structure this is especially important
because the smallest interatomic distance between atoms of the same and atoms
of different layers is different, but both distances are comparable.
This leads to a different number of peaks in the spectra which might help to
distinguish between clusters of icosahedral and cuboctahedral cluster structure.

While the theoretical lifetime of the bulk atoms show an excellent agreement
with experiment, the lifetimes of the surface atoms differ significantly.
This deviation
might be caused by different static cluster structures than taken into account
in this work, by different energetic stabilization of charges or by nuclear
dynamics. Which of these reasons explains the experiment can not be determined
at the moment. Experimentally determined photoelectron spectra of the outer
valence of high resolution in neon clusters would help to solve this puzzle.
